The \project{UNRAVE} catalog

### 2016-08-15 article/unrave.tex
and MS

\author{Some combination of: Harry Enke, Gerry Gilmore, Keith Hawkins, David W. Hogg, Gal Matijevic, Melissa Ness, Jason Sanders, Hans Walter-Rix, and any other  \project{RAVE} people who have contributed to the data analysis}
%\altaffiltext{3}{\texttt{arc@ast.cam.ac.uk}}

>>>>

\author{Some combination of: Harry Enke, Gerry Gilmore, Keith Hawkins, David W. Hogg, Gal Matijevic, Melissa Ness, Jason Sanders, Matthias Steinmetz, Hans Walter-Rix, and any other \project{RAVE} people who have contributed to the data analysis}
%\altaffiltext{3}{\texttt{arc@ast.cam.ac.uk}}
